\documentclass[10pt]{beamer}

\usetheme{Madrid}
\usecolortheme{seahorse}

% ---------- ICONS ----------
\usepackage{fontawesome}

% ---------- CLEAN CORPORATE BACKGROUND ----------
\usepackage{tikz}
\usebackgroundtemplate{
\begin{tikzpicture}[remember picture,overlay]
  % Deep corporate navy gradient
  \path[shade, top color=black!98, bottom color=blue!25!black]
    (current page.south west) rectangle (current page.north east);
\end{tikzpicture}
}

% ---------- CORPORATE COLORS ----------
\setbeamercolor{normal text}{fg=white}
\setbeamercolor{frametitle}{fg=cyan}
\setbeamercolor{title}{fg=cyan}
\setbeamercolor{structure}{fg=cyan}

% Professional block styling
\setbeamercolor{block title}{bg=cyan!18, fg=white}
\setbeamercolor{block body}{bg=black!35, fg=white}

% Remove navigation symbols
\setbeamertemplate{navigation symbols}{}

% ---------- META ----------
\title{Student Survival System (SSS)}
\subtitle{Real-Time Verified Support Platform for Students}
\author{Anurag \quad | \quad Vineet | \quad Jitendra \quad | \quad Asgar}
\institute{B.Tech CSE \\ Section 2 \\ Institute Of Engineering And TechnologymainLucknow}
\date{}

\begin{document}

%------------------ Slide 1 ------------------
\begin{frame}
\titlepage
\vspace{0.3cm}
\centering
\textcolor{cyan!70}{\faLock \;\; Verified Reviews \;\;|\;\; \faBellO \;\; Real-Time Complaints \;\;|\;\; \faLineChart \;\; Risk Badge}
\end{frame}

%------------------ Slide 2 ------------------
\begin{frame}{\faExclamationTriangle \;\; Problem Statement}
\begin{itemize}
    \item[\faHome] Students face difficulty finding reliable PG/Rooms near college.
    \item[\faUser] Reviews are often fake or outdated.
    \item[\faBug] No real-time issue reporting system.
    \item[\faLock] No verification or confirmation mechanism.
\end{itemize}
\end{frame}

%------------------ Slide 3 ------------------
\begin{frame}{\faLightbulbO \;\; Proposed Solution}
\begin{itemize}
    \item[\faMapMarker] PG listing with price, distance, contact and map.
    \item[\faUser] Login-based verified student reviews.
    \item[\faCommentsO] Complaint system with peer confirmation.
    \item[\faLineChart] Risk badge based on real-time activity.
    \item[\faCogs] Admin moderation system.
\end{itemize}
\end{frame}

%------------------ Slide 4 ------------------
\begin{frame}{\faExchange \;\; Comparison}
\begin{columns}

\column{0.48\textwidth}
\begin{block}{\faGlobe \;\; Existing Platforms}
\begin{itemize}
    \item Open public reviews
    \item No confirmation mechanism
    \item Static listings
    \item No risk analysis
\end{itemize}
\end{block}

\column{0.48\textwidth}
\begin{block}{\faLock \;\; SSS}
\begin{itemize}
    \item Authorized login access
    \item Complaint confirmation system
    \item Real-time reporting
    \item Risk level indication
    \item Admin moderation
\end{itemize}
\end{block}

\end{columns}
\end{frame}

%------------------ Slide 5 ------------------
\begin{frame}{\faWrench \;\; Technology Stack}
\begin{itemize}
    \item[\faDesktop] Frontend: HTML, CSS, JavaScript, React (CDN)
    \item[\faServer] Backend: PHP (XAMPP)
    \item[\faDatabase] Database: MySQL
    \item[\faMapMarker] Google Maps API
    \item[\faCodeFork] GitHub
\end{itemize}
\end{frame}

%------------------ Slide 6 ------------------
\begin{frame}{\faClockO \;\; Timeline \& Status}
\begin{columns}
\column{0.5\textwidth}
\begin{block}{Timeline}
\begin{itemize}
    \item Week 1: Database + PG module
    \item Week 2: Login + Reviews
    \item Week 3: Admin + Risk logic
\end{itemize}
\end{block}

\column{0.5\textwidth}
\begin{block}{Current Status}
\begin{itemize}
    \item PG module completed
    \item Login system working
    \item Admin dashboard functional
    \item Future modules planned
\end{itemize}
\end{block}
\end{columns}
\end{frame}

%------------------ Slide 7 ------------------
\begin{frame}{\faRocket \;\; Future Scope}
\begin{itemize}
    \item[\faCutlery] Food availability module
    \item[\faMedkit] Medical emergency support
    \item[\faMoney] Expense tracking
    \item[\faBellO] Smart alerts
\end{itemize}
\end{frame}

%------------------ Slide 8 ------------------
\begin{frame}{\faFlagCheckered \;\; Conclusion}
\begin{itemize}
    \item[\faLock] Improves trust using verified login.
    \item[\faCheckCircle] Reduces fake reviews.
    \item[\faLineChart] Enables safer PG selection.
\end{itemize}

\centering
\vspace{0.3cm}
\textcolor{cyan!70}{\Large \faThumbsUp \;\; Thank You}
\end{frame}

\end{document}
